---
title: "Par"
date: "March 31, 2016"
output: html_document
---

# bg

### Description:

"The color to be used for the background."

### Mnemonic: 

**B**ack**G**round

```{r echo=FALSE}
set.seed(3-31-2016)
opar <- par(no.readonly=TRUE)
```

```{r}
par(bg = "blue")
plot(rnorm(100))

par(bg = "#F0F0F0")
plot(rnorm(100))

par(bg = "#DCE6EC")
plot(rnorm(100))
```

```{r echo=FALSE}
par(opar)
```

# bty

### Description:

"A string which determines the type of box which is drawn around plots."

### Mnemonic: 

**B**ox **TY**pe

```{r}
par(bty = "o")
plot(rnorm(100))


par(bty = "l")
plot(rnorm(100))

par(bty = "7")
plot(rnorm(100))

par(bty = "c")
plot(rnorm(100))

par(bty = "u")
plot(rnorm(100))

par(bty = "]")
plot(rnorm(100))

par(bty = "n")
plot(rnorm(100))
```

```{r echo=FALSE}
par(opar)
```

# cex

### Description:

"A number specifiying the amount by which plotting text and symbols should be magnified."

### Mnemonic: 

**C**haracter **EX**pansion

```{r}
par(cex = 2)
plot(rnorm(100))

par(cex = .5)
plot(rnorm(100))
```

```{r echo=FALSE}
par(opar)
```

# cex.axis

### Description:

"A number specifiying the amount by which plotting text and symbols should be magnified."

### Mnemonic: 

**C**haracter **EX**pansion

```{r}
par(cex = 1, cex.axis = 0.5)
plot(rnorm(100))

par(cex = 1, cex.axis = 2)
plot(rnorm(100))
```

```{r echo=FALSE}
par(opar)
```

# cex.main

```{r}
par(cex = 1, cex.main = 0.5)
plot(rnorm(100))

par(cex = 1, cex.main = 2)
plot(rnorm(100))
```

```{r echo=FALSE}
par(opar)
```

# family

### Description:

"The name of a font family for drawing text."

```{r}
par(family = "mono")
plot(rnorm(100))

par(family = "serif")
plot(rnorm(100))
```

```{r echo=FALSE}
par(opar)
```

# fg

### Description:

"The color to be used for the foreground of plots."

### Mnemonic: 

**F**ore**G**round

```{r}
par(fg = "red")
plot(rnorm(100))
```

```{r echo=FALSE}
par(opar)
```

# fg

### Description:

"The color to be used for the foreground of plots."

### Mnemonic: 

**F**ore**G**round

```{r}
par(fg = "red")
plot(rnorm(100))
```

```{r echo=FALSE}
par(opar)
```