---
title: "Par"
date: "March 31, 2016"
output: html_document
---

# bg

### Description:

"The color to be used for the background."

### Mnemonic: 

**B**ack**G**round

```{r}
set.seed(3-31-2016)
opar <- par(no.readonly=TRUE)
```

```{r}
par(bg = "blue")
plot(rnorm(100))

par(bg = "#F0F0F0")
plot(rnorm(100))

par(bg = "#DCE6EC")
plot(rnorm(100))
```

```{r echo=FALSE}
par(opar)
```

# bty

### Description:

"A string which determines the type of box which is drawn around plots."

### Mnemonic: 

**B**ox **TY**pe

```{r}
par(bty = "o")
plot(rnorm(100))


par(bty = "l")
plot(rnorm(100))

par(bty = "7")
plot(rnorm(100))

par(bty = "c")
plot(rnorm(100))

par(bty = "u")
plot(rnorm(100))

par(bty = "]")
plot(rnorm(100))

par(bty = "n")
plot(rnorm(100))
```

```{r echo=FALSE}
par(opar)
```

# cex

### Description:

"A number specifiying the amount by which plotting text and symbols should be magnified."

### Mnemonic: 

**C**haracter **EX**pansion

```{r}
par(cex = 2)
plot(rnorm(100))

par(cex = .5)
plot(rnorm(100))
```

```{r echo=FALSE}
par(opar)
```

# cex.axis

### Description:

"A number specifiying the amount by which plotting text and symbols should be magnified."

### Mnemonic: 

**C**haracter **EX**pansion

```{r}
par(cex = 1, cex.axis = 0.5)
plot(rnorm(100))

par(cex = 1, cex.axis = 2)
plot(rnorm(100))
```

```{r echo=FALSE}
par(opar)
```

# cex.main

```{r}
par(cex = 1, cex.main = 0.5)
plot(rnorm(100))

par(cex = 1, cex.main = 2)
plot(rnorm(100))
```

```{r echo=FALSE}
par(opar)
```

# family

### Description:

"The name of a font family for drawing text."

```{r}
par(family = "mono")
plot(rnorm(100))

par(family = "serif")
plot(rnorm(100))
```

```{r echo=FALSE}
par(opar)
```

# fg

### Description:

"The color to be used for the foreground of plots."

### Mnemonic: 

**F**ore**G**round

```{r}
par(fg = "red")
plot(rnorm(100))
```

```{r echo=FALSE}
par(opar)
```

# font

### Description:

"An integer which specifies which font to use."

```{r}
par(font = 2)
plot(rnorm(100))
mtext("Text")

par(font = 3)
plot(rnorm(100))
mtext("Text")

par(font = 4)
plot(rnorm(100))
mtext("Text")

par(font = 5)
plot(rnorm(100))
mtext("Text")
```

```{r echo=FALSE}
par(opar)
```

# lab

### Description:

"A numerical vector of the form c(x, y, len) which modifies
the default way that axes are annotated."

### Mnemonic: 

**LAB**el length

```{r}
par(lab = c(10, 3, 7))
plot(rnorm(100))

par(lab = c(40, 20, 7))
plot(rnorm(100))
```

```{r echo=FALSE}
par(opar)
```

# las

### Description:

"The style of axis labels."

### Mnemonic: 

**LA**bel **S**tyle

```{r}
par(las = 0)
plot(rnorm(100))

par(las = 1)
plot(rnorm(100))

par(las = 2)
plot(rnorm(100))

par(las = 3)
plot(rnorm(100))
```

```{r echo=FALSE}
par(opar)
```

# lty

### Description:

"The line type."

### Mnemonic: 

**L**ine **TY**pe

```{r}
plot(rnorm(100), type = "l", lty = 2)
plot(rnorm(100), type = "l", lty = 3)
plot(rnorm(100), type = "l", lty = 6)
```

```{r echo=FALSE}
par(opar)
```

# lwd

### Description:

"The line width."

### Mnemonic: 

**L**ine **W**i**D**th

```{r}
plot(rnorm(100), type = "l", lwd = 1)
plot(rnorm(100), type = "l", lwd = 2)
plot(rnorm(100), type = "l", lwd = 5)
```

```{r echo=FALSE}
par(opar)
```

# mai

### Description:

"The margin size."

### Mnemonic: 

**MA**rgin s*I*ze

```{r}
par(mai = c(0, opar$mai[2:4]))
plot(rnorm(100))

par(mai = c(opar$mai[1], 0, opar$mai[3:4]))
plot(rnorm(100))

par(mai = c(opar$mai[1:2], 0, opar$mai[4]))
plot(rnorm(100))

par(mai = c(opar$mai[1:3], 0))
plot(rnorm(100))
```

```{r echo=FALSE}
par(opar)
```

# mar

### Description:

"The number of margin lines on the four sides of the plot."

### Mnemonic: 

**MAR**rgin lines

```{r}
par(mar = c(0, 4, 4, 2) + 0.1)
plot(rnorm(100))

par(mar = c(5, 0, 4, 2) + 0.1)
plot(rnorm(100))

par(mar = c(5, 4, 0, 2) + 0.1)
plot(rnorm(100))

par(mar = c(5, 4, 4, 0) + 0.1)
plot(rnorm(100))
```

```{r echo=FALSE}
par(opar)
```

# mfrow

### Description:

"A vector of the form c(nr, nc). Subsequent figures will be drawn in an nr-by-nc array by columns (mfcol), or rows (mfrow), respectively."

### Mnemonic: 

```{r}
par(mfrow = c(2, 2))
replicate(4, plot(rnorm(100)))

par(mfrow = c(2, 1))
replicate(2, plot(rnorm(100)))

par(mfrow = c(1, 2))
replicate(2, plot(rnorm(100)))

par(mfrow = c(3, 2))
replicate(6, plot(rnorm(100)))
```

```{r echo=FALSE}
par(opar)
```

# tcl

### Description:

"The length of tick marks as a fraction of the height of a line of text."

### Mnemonic: 

**T**i**C**k **L**ine

```{r}
par(tcl = 1)
plot(rnorm(100))

par(tcl = -1)
plot(rnorm(100))

par(tcl = -0.1)
plot(rnorm(100))
```

```{r echo=FALSE}
par(opar)
```